---
title: "Environmental Protection is What We Care About!"
author: "Yuyan Xu"
date: 2020-09-26T21:13:14-05:00
bibliography: references.bib
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(visdat)
library(cesR)
library(skimr)
library(dplyr)
```
#Abstract
Based on the analyze of the Campaign Period Survey (the CPS) completed in 2008, voters value the environment protection and they seem to expect the leader to pay more attention in environmental issue, along with health care system.

# Introduction
In this repot, I investigated the 2008 CES dataset (@cesR), which is short for Canadian Election Study. The CES consists 3 surveys that were conducted during the second half of the election campaign and there were about 4500 eligible voters participated in the survey. This dataset effectively reflects the politics of scale of Canadaian voters, and how they generally expect from the country leader.

There were 3 surveys completed: Campaign Period Survey, Post Election Survey and Mailback Survey. As their names suggested, these surveys were taken at different times around the time of 2008 Canadian Election. All surveys were completed by respondents via web, mail or telephone.I chose to  focus on the data provided by the campaign period survey (the CPS) due to a large number of variables and observations. An interesting finding of my investigation on this particular subset of data was, a majority of respondents seems to value the environment a lot, which shows that environment protection could be an influential factor in how they vote during election. In fact, when the respondents were asked “What is the most important issue to YOU PERSONALLY in this FEDERAL election? ”, about 10 percent of them chose “environmental/ecological issue”.

Due to a large amount of nonresponses, the findings of this report might not truly reflect on the population of voters. 

# Data and Findings

```{r download, warning=FALSE, message=FALSE}
devtools::install_github("hodgettsp/cesR")
cesR::get_ces(srvy = 'ces2008')

```

So firstly, I created a subset of CES2008 dataset, which randomly select 45 variables and 1000 observations from each of them. The package visdat (@visdat) gives us a visual representation of the presented data, the grey area are the missing data (nonresponse datapoints). From the graph we can see that the grey area is pretty large, this means there are a fairly amount of nonresponsive answer in the survey. For this issue, I use vis_miss() function to find out the percentage of the missing data, which is 42.1%. This is quite a lot.
The functions glimpse() (@dplyr) and skim() (@skimr) gave me a summary of the data information: there are 45 variables with 4495 observations. The variables can be categorized as discrete and numeric, in this subset of data, there are 33 discrete variables and 12 numeric variables. 

```{r, warning=FALSE, message = FALSE}
#Sample size and number of varibales are too large, randomly select 45 variables and look at the <= 1000 observations for each of them.
subset_2008 <- select(ces2008, 26:70)
subset_2008 %>%
  sample_n(1000) %>%
  vis_dat()
vis_miss(subset_2008, cluster = FALSE, sort_miss = FALSE, show_perc = TRUE,
show_perc_col = TRUE, large_data_size = 9e+05, warn_large_data = TRUE)
glimpse(subset_2008)
skimr::skim(subset_2008)

```

The variables I chose to focus were the discrete variables: ces08_CPS_I4 (Importance: Protecting the environment?) and ces08_CPS_A2 (What is the most important issue to YOU PERSONALLY in this FEDERAL election?). This is because, from the data summary above, ces08_CPS_I4 had the highest completion rate with 72.1%. Also, the reason I chose ces08_CPS_A2 was to investigate whether environment protection is one of the major factors that Canadians took into considerations when they vote. At the same time, ces08_CPS_A2 had a completion rate of 61.9%, not so bad.


Then, I used filter() (@dplyr) to filter out all the respondents that chose option 1 for ces08_CPS_I4, which means they thought environment protection is very important. Then, I created a data summary for ces08_CPS_A2 in this particular subset. Also, I used select() (@dplyr) to select out these two variables and compare their statistics alone. As we can see here, ces_CPS_I4 has a median of 1 and the mean is 1.3, this means a lot of people chose option 1. For ces08_CPS_A2 though, the mean is 48 and median is 57, so far, not much can tell from this.

```{r}
#Look at the data summary of ces08_CPS_A2 in the subset of people chose "very important" or "somewhat important" in ces08_CPS_I4.
subset2_2008 <- 
  subset_2008 %>% 
  filter(ces08_CPS_I4 <= 2)
summary(subset2_2008$ces08_CPS_A2)
#Compare the data summaries of both of the variables.
subset3_2008 <- 
  subset_2008 %>% 
  select(ces08_CPS_I4,ces08_CPS_A2)
summary(subset3_2008)

```


I created histograms and bar graphs for each of the two variables.

```{r}
#Histograms
subset_2008 %>% 
  ggplot(aes(x = ces08_CPS_I4)) +
  geom_histogram(binwidth = 0.5)

subset_2008 %>% 
  ggplot(aes(x = ces08_CPS_A2)) +
  geom_histogram(binwidth = 0.5)
```

```{r}
#Bar Graphs
subset_2008 %>% 
  ggplot(aes(x = ces08_CPS_I4)) +
  geom_bar()

subset_2008 %>% 
  ggplot(aes(x = ces08_CPS_A2)) +
  geom_bar()
  
```

In the histogram below I find that the distribution of how people view of environment protection heavily skewed towards "very important". 

```{r}
subset_2008 %>% 
  ggplot(aes(x = ces08_CPS_I4)) +
  geom_histogram()+
  labs(x = "Degree of Agreeance",
       y = "Number",
       title = "Distribution of agreement in the importance of protecting environment in 2008 CES",
       caption = "Source: Gidengil, E, Everitt, J, Fournier, P and Nevitte, N. 2009.") +
  theme_bw()
```


#Discussion
From the graphs above, there were over 3000 people voted "very important" and "somewhat important" when they were asked the level of importance in protecting environment; and about 300 people voted that they considered environmental/ecological issue as the most imporant issue during the federal election. One thing worth mentioning about the dataset was, there were over 600 people voted "economy issues" was the most important issue to them personally; and there were over 500 people voted "health care issues". The "environmental issues" ranked the third in this question.

It shows that environemntal problem has became a huge topic that grab a lot of attention not only from many governmental authorities, but also from the general citizens. It is one of the most influential factors when Canadian citizens vote during federal election.

#Weaknesses and next steps
This report has several weaknesses that need to be paid attention in future study. First, only 45 variables were chosen to analyze while there is a total of 541 variables in the dataset. This means that the statistical summaries in this report is not thorough enough and the final finding might not be accurate; Second, in the original survey dataset, there are about 42% of the observations missing, which means respondents did not response to some particular questions. This could result in response bias, which might result in inaccurate findings as well. This problem could be avoided if there are fewer questions included in the survey, because I think people’s interests would likely wore down while they are taking the survey with too many questions.


#References
-Gidengil, E, Everitt, J, Fournier, P and Nevitte, N. 2009. The 2008 Canadian Election Study [dataset]. Toronto, Ontario, Canada: Institute for Social Research [producer and distributor].

- Paul A. Hodgetts and Rohan Alexander (2020). cesR: Access the CES Datasets a Little Easier.. R package version 0.1.0.

-  Hadley Wickham, Jim Hester and Winston Chang (2020). devtools: Tools to Make Developing R Packages Easier. https://devtools.r-lib.org/,https://github.com/r-lib/devtools.

- R Core Team (2020). R: A language and environment for statistical computing. R, Foundation for Statistical Computing, Vienna, Austria. URL, https://www.R-project.org/.

- JJ Allaire and Yihui Xie and Jonathan McPherson and Javier Luraschi and Kevin Ushey and Aron Atkins and Hadley Wickham and Joe Cheng and Winston Chang and Richard Iannone (2020). rmarkdown: Dynamic Documents for R. R package version 2.3. URL https://rmarkdown.rstudio.com.

- R packages. Using Visdat. https://cran.r-project.org/web/packages/visdat/vignettes/using_visdat.html
